Complete Real-Time Liver Model including Glisson Capsule, Vascular Network and Parenchyma

### 2013-03-01 Doc/Miccai2013/miccai2013.tex
adding references
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@537 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

\begin{document}
%
%\frontmatter          % for the preliminaries
%
\mainmatter              % start of the contributions
%
\title{Complete Real-Time Liver Model including Glisson Capsule, Vascular Network and Parenchyma}
%
\titlerunning{TODO: Title}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Anonymous}
%\author{%
%Tom\'a\v{s} Golembiovsk\'y\inst{1,2} \and%
%Igor Peterl\'ik\inst{3} \and%
%Christian Duriez\inst{2} \and%
%Stephan\'e Cotin\inst{2,3}%
%}
%
%\authorrunning{Tom\'a\vs Golembiovsk\'y et al.} % abbreviated author list (for running head)
%
%\institute{%
%Faculty of Informatics, Masaryk University, Brno, Czech Republic\and%
%INRIA Lille -- Nord, France\and%
%IHU, Strasbourg, France%
%}
%
\maketitle

@@

In case of human liver, the task of real-time accurate modeling is challenging, mainly because of the complex structure 
of this organ composed of three main constituents: \emph{parenchyma}, \emph{vascular networks} and \emph{Glisson's capsule}.
The parenchyma has certainly been the most studied component of the liver; today the researchers agree on hyperelastic 
properties of the tissue, for which the mechanical parameters have been reported for example in~\cite{}\TODO. 
Several methods have been proposed to model the hyperelastic behaviour at real-time rates, such as multiplicative Jacobian decomposition
introduced in~\cite{Marchesseau2010}.

@@

The computation of elastic stiffness matrix follows the common derivation
%
\begin{eqnarray}
  \Mat{K^m} & = \int_V \Mat{B}^T \Mat{E} \Mat{B} dV     \label{mem1} \\
            & = h \int_A \Mat{B}^T \Mat{E} \Mat{B} dA   \label{mem2} \\
            & = h A \Mat{B}^T \Mat{E} \Mat{B}           \label{mem3}
\end{eqnarray}
%
where $\Mat{B}$ is the strain-displacement matrix, $\Mat{E}$ the material
matrix, $h$ is the thickness and $A$ area of the element. In the previous
\eqref{mem2} follows from the fact that we assume constant thickness of the
element and \eqref{mem3} follows from the fact that the strain-displacement
matrix is in our case constant. The strain-displacement matrix for the CST
element can be expressed as:

@@

\IP{we have to also add some information how we got the models -- either we comment briefly in each subsection:
Local deformations: cube meshed in gmsh (graded mesh?), number of elements, etc...
Global deformations: contrast-enhanced CT data obtained via acquisition performed on a female pig; the 3D mesh created by a
semi-automatic segmentation using ITKSnap~\cite{itksnap}, then meshed using CGAL~\cite{cgal-meshingAlg} resulting in a mesh having 
NNN elements. The capsule modelled using the surface triangular elements extracted from the tetrahedra. The vascularization 
created from the segmentation of hepatic vein as described in~\cite{Peterlik2012}. The structured composed of MMM elements.}
\TG{Sure. Put it here or into the respective subsections? (cube: graded
  mesh created by gmsh with 2648 tetrahedra, 518 triangles for capsule
extracted from tetrahedral mesh.)}

>>>>

\begin{document}
%
%\frontmatter          % for the preliminaries
%
\mainmatter              % start of the contributions
%
\title{Complete Real-Time Liver Model including Glisson Capsule, Vascular Network and Parenchyma}
%
\titlerunning{Complete Liver Model}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Anonymous}
%\author{%
%Tom\'a\v{s} Golembiovsk\'y\inst{1,2} \and%
%Igor Peterl\'ik\inst{3} \and%
%Christian Duriez\inst{2} \and%
%Stephan\'e Cotin\inst{2,3}%
%}
%
%\authorrunning{Tom\'a\vs Golembiovsk\'y et al.} % abbreviated author list (for running head)
%
%\institute{%
%Faculty of Informatics, Masaryk University, Brno, Czech Republic\and%
%INRIA Lille -- Nord, France\and%
%IHU, Strasbourg, France%
%}
%
\maketitle

@@

In case of human liver, the task of real-time accurate modeling is challenging, mainly because of the complex structure 
of this organ composed of three main constituents: \emph{parenchyma}, \emph{vascular networks} and \emph{Glisson's capsule}.
The parenchyma has certainly been the most studied component of the liver; today the researchers agree on hyperelastic 
properties of the tissue, for which the mechanical parameters have been reported for example in~\cite{Kerdok2006,Gao2009}. 
Several methods have been proposed to model the hyperelastic behaviour at real-time rates, such as multiplicative Jacobian decomposition
introduced in~\cite{Marchesseau2010}.

@@

The computation of elastic stiffness matrix follows the common derivation

\begin{eqnarray}
  \Mat{K}^m & = \int_V \Mat{B}^T \Mat{E} \Mat{B} dV     \label{mem1} \\
            & = h \int_A \Mat{B}^T \Mat{E} \Mat{B} dA   \label{mem2} \\
            & = h A \Mat{B}^T \Mat{E} \Mat{B}           \label{mem3}
\end{eqnarray}

where $\Mat{B}$ is the strain-displacement matrix, $\Mat{E}$ the material
matrix, $h$ is the thickness and $A$ area of the element. In the previous
\eqref{mem2} follows from the fact that we assume constant thickness of the
element and \eqref{mem3} follows from the fact that the strain-displacement
matrix is in our case constant. The strain-displacement matrix for the CST
element can be expressed as:

@@

\IP{we have to also add some information how we got the models -- either we comment briefly in each subsection:
Local deformations: cube meshed in gmsh (graded mesh?), number of elements, etc...
Global deformations: contrast-enhanced CT data obtained via acquisition performed on a female pig; the 3D mesh created by a
semi-automatic segmentation using ITKSnap\footnote{www.itksnap.org}, then meshed using CGAL\footnote{www.cgal.org} \cite{Boltcheva2009} resulting in a mesh having 
NNN elements. The capsule modelled using the surface triangular elements extracted from the tetrahedra. The vascularization 
created from the segmentation of hepatic vein as described in~\cite{Peterlik2012}. The structured composed of MMM elements.}
\TG{Sure. Put it here or into the respective subsections? (cube: graded
  mesh created by gmsh with 2648 tetrahedra, 518 triangles for capsule
extracted from tetrahedral mesh.)}
